Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_wrapping.tex
removed "Kassel"
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@870 d8b0c59b-6544-0410-94d9-83a5658a058e
some corrections
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@873 d8b0c59b-6544-0410-94d9-83a5658a058e

\section{Wrapping web services (Kassel)}
\label{sec:wrapping_web_services}

@@

If needed, a detailed specification of the Ebay Shopping API can be found at \cite{eBayShoppingAPIs}.

@@

Figure~\ref{fig:construct_service_request} shows the web based tool to construct the service requests.

@@

In the top input field of Figure ~\ref{fig:construct_service_request}, the user may drop an example HTTP request taken e.g. form the service documentation e.g. from its website\footnote{http://developer.ebay.com/products/shopping/}. The tool analyses the example request and in the middle of the screen a form for editing the request parameters is provided. In our example, the user has connected the \textit{QueryKeywords} parameter with the input parameter \textit{search\_key} by adding a corresponding reference to the value field of that parameter. In addition, we have retrieved an access key which has been entered as value for the \textit{appid} parameter.

>>>>

\section{Wrapping web services}
\label{sec:wrapping_web_services}

@@

@@

An example of service request construction can be found in the Figure~\ref{fig:construct_service_request}. In the top input field the user may drop an example HTTP request taken e.g. form the service documentation e.g. from its website\footnote{http://developer.ebay.com/products/shopping/}. The tool analyses the example request and in the middle of the screen a form for editing the request parameters is provided. In our example, the user has connected the \textit{QueryKeywords} parameter with the input parameter \textit{search\_key} by adding a corresponding reference to the value field of that parameter. In addition, we have retrieved an access key which has been entered as value for the \textit{appid} parameter.

@@
